---
title: "CodeBookRMD"
author: "Nadia Stavisky"
date: "5/5/2019"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Full description is available at the Human Activity Recognition Using
Smartphones Data Set
site. See <http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones>

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
setwd("/Users/Nadya/Nanodegree/Data Science Specialization/Getting and Cleaning Data")
data <- read.table("./project4/tidy_data.txt")
```

Data dimensions
Number of observations:
```{r, echo=FALSE}
dim(data)[1]
```
Number of variables:
```{r, echo=FALSE}
dim(data)[2]
```
Data structure:
```{r, echo=FALSE}
str(data)
```
Measurments transformed into average of the mean and
    standard deviation for each measurement from the raw data set for
    each activity and each subject.

Variables Data grouped by:
```{r, echo=FALSE}
colnames(data)[1:2]
```
Time domain signals:
```{r, echo=FALSE}
measurments <- colnames(data)[-c(1:2)]
measurments[grep("^time", measurments)]
```

Frequency domain signals:
```{r, echo=FALSE}
measurments <- colnames(data)[-c(1:2)]
measurments[grep("^frequency", measurments)]
```

